Unlocking Accountability: A Mixed-Methods Analysis of Bottom-Up Approaches in Brazilian Public Policy

### 2023-10-27 Scripts/paper.Rmd
Correção em contagem de obras do OT e repercussões

lista_cidades_ot <- c("Araucária", "Caçador", "Campo Mourão", "Cascavel", "Chapecó",
                      "Foz do Iguaçu", "Goioerê", "Gravataí", "Guarapuava", "Imbituba", "Lajeado",
                      "Limeira", "Palhoça", "Paranaguá", "Pelotas", "Ponta Grossa", "Santa Maria",
                      "São Francisco do Sul", "São José dos Campos", "Taubaté", "Uberlândia")

df_cidades_ot <- data.frame(municipio = lista_cidades_ot, indicator_ot = 1)

@@

load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
```

@@

obras_inicio_projeto_ot <- obras_inicio_projeto %>%
  left_join(df_cidades_ot, by="municipio")

@@

antes_projeto <- obras_inicio_projeto_ot %>%
  group_by(indicator_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
         total = sum(contagem),
         perc = round(contagem/total, 2))

@@

obras_fim_seg_fase <- obras_fim_seg_fase %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao))) %>%
  left_join(df_cidades_ot, by="municipio") %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot))

depois_projeto <- obras_fim_seg_fase %>%
  group_by(indicator_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(total = sum(contagem),
         perc = round(contagem/total, 2))

@@

```{r tables, echo=FALSE, message=FALSE, results='asis'}
antes_projeto %>%
  gt() %>%
  tab_header(
    title = "Percentage of finished fonstruction works before the project",
    subtitle = "Situation in August 2017") %>%
  cols_label(
    indicator_ot = "Obra Transparente Indicator",
    perc = "Percentage of finished constructions"
  )
```

@@

df_balancing_aux <- obras_inicio_projeto_ot %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
         perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc))
df_balancing <- df_balancing_aux %>%
  distinct(code_muni, .keep_all = TRUE)

@@

```{r balancing check, message=FALSE, echo=FALSE}
m.out <- matchit(indicator_ot ~ perc_pea18  + ext_pobres  + log_rpc + 
                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
                  log_renda + log_pop, data = df_balancing,
                 replace = TRUE, ratio = 3)

# summary(m.out)
# summary(m.out, un=FALSE)
# plot(m.out, type = "jitter", interactive = FALSE)
# 
# m.sum <- summary(m.out)
# 
# plot(m.sum, var.order = "unmatched")

>>>>

# lista_cidades_ot <- c("Araucária", "Caçador", "Campo Mourão", "Cascavel", "Chapecó",
#                       "Foz do Iguaçu", "Goioerê", "Gravataí", "Guarapuava", "Imbituba", "Lajeado",
#                       "Limeira", "Palhoça", "Paranaguá", "Pelotas", "Ponta Grossa", "Santa Maria",
#                       "São Francisco do Sul", "São José dos Campos", "Taubaté", "Uberlândia")
# 
# df_cidades_ot <- data.frame(municipio = lista_cidades_ot, indicator_ot = 1)

@@

load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))

df_cidades_ot <- read_excel("Dados/181114 - Situação obras_atual.xlsx", 
                                           sheet = "SIMEC-Mai17", skip = 1) %>%
  clean_names() %>%
  filter(!is.na(id)) %>%
  dplyr::select(id, municipio, uf, situacao2, levant_os_jun_17) %>%
  mutate(indicator_ot = 1)
```

@@

obras_inicio_projeto_ot <- obras_inicio_projeto %>%
  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id"))

@@

aux_indicator_ot <- df_cidades_ot %>%
  distinct(municipio, uf) %>%
  mutate(indicator_muni_ot = 1)

obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))

antes_projeto <- obras_inicio_projeto_ot %>%
  group_by(indicator_muni_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(total = sum(contagem),
         perc = round(contagem/total, 2))

@@

obras_fim_seg_fase <- obras_fim_seg_fase %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao)),
         id = as.numeric(id)) %>%
  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id")) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))

depois_projeto <- obras_fim_seg_fase %>%
  group_by(indicator_muni_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(total = sum(contagem),
         perc = round(contagem/total, 2))

@@

```{r tables, echo=FALSE, message=FALSE, results='asis'}
antes_projeto %>%
  gt() %>%
  tab_header(
    title = "Percentage of finished fonstruction works before the project",
    subtitle = "Situation in August 2017") %>%
  cols_label(
    indicator_muni_ot = "Participating Municipalities in Obra Transparente ",
    perc = "Percentage of Completed Constructions"
  ) %>%
    fmt_percent(
    columns = perc,
    decimals = 0
  )
```

@@

df_balancing_aux <- obras_inicio_projeto_ot %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
         perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc),
         tipo_do_projeto = ifelse(grepl("Bloco Estrutural" ,tipo_do_projeto),
                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto))

df_balancing_aux %>%
  group_by(tipo_do_projeto) %>%
  summarise(n())

@@

```{r balancing check, message=FALSE, echo=FALSE}
m.out <- matchit(indicator_ot ~ perc_pea18  + ext_pobres  + log_rpc + 
                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
                  log_renda + log_pop + percentual_de_execucao + rede_de_ensino_publico + tipo_do_projeto , data = df_balancing,
                 replace = TRUE, ratio = 3)

summary(m.out)
# summary(m.out, un=FALSE)
# plot(m.out, type = "jitter", interactive = FALSE)
# 
# m.sum <- summary(m.out)
# 
# plot(m.sum, var.order = "unmatched")
